FoRTE baseline

### 2019-07-23 analysis/paper/paper.Rmd
Write second methods paragraph

```{r pairs-time, fig.cap = pairs_time_cap, fig.dim = c(8, 8)}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type.",
  "Letter labels are selected runs with the same parameters,",
  "and match the rows in Figure 4. The characteristics of these poitns are",
  "as follows:",
  "(A) high NPP and LAI, and relatively high pine LAI;",
  "(B) high Shannon diversity;",
  "(C) close to observed NPP and LAI values;",
  "(D) high early hardwood LAI",
  "(E) high late hardwood LAI."
)
readd(pairs_time_averaged)
```

In most simulations, the leaf area index was usually too low for a given level of net primary productivity, but the relationship between these two variables varied with model configuration (Figure 3).
The crown model (closed vs. finite) had the strongest effect: Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Only a few simulations matched _both_ the observed leaf area index and net primary productivity, and all of them had the finite canopy radius configuration.

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 8)}
bigfacet_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3."
)
readd(lai_pft_plot)
```

@@

Model structure and parameters interacted in determining the community assembly and dynamics of each simulation (Figure 4).
Generally, the highest net primary productivity and leaf area index values (averaged across growing seasons from 1975 to 2000) occurred in runs dominated by pine.
With the exception of the configuration with finite canopy radius and two-stream radiative transfer (under which most simulations had near-zero productivity), parameter values were more important to determining the ecological trajectory than model configuration.
For example, all model configurations in parameter combination _E_ saw immediate and total dominance by late hardwood followed by eventual die-off.
However, the magnitude of peak leaf area index and the pace of the subsequent die-off varied with model configuration, with a smaller peak and slower die-off under a finite canopy compared to the default closed canopy.

@@

Across all variables, parameter uncertainty (across ensembles within each model configuration) was at least as large, and usually larger, than structural uncertainty (Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question. 
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) led to reduced predictive uncertainty for all four variables considered, with the largest uncertainty reduction for gross and net primary productivity.
Meanwhile, facilitating horizontal competition by enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) substantially reduced uncertainty in aboveground biomass and diversity, and slightly reduced uncertainty in gross and net primary productivity.
Finally, using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased uncertainty in leaf area index, aboveground biomass, and diversity, but did not have a consistent effect on uncertainty in predictions of productivity.

```{r uncertainty-analysis, fig.cap = uncertainty_analysis_cap, fig.dim = c(15, 15)}
uncertainty_analysis_cap <- paste(
  htmlfig(),
  "PEcAn-like parameter sensitivity and uncertainty analysis, by model type.",
  "Elasticity (a, b) is the normalized sensitivity of the model to a fixed change in the parameter.",
  "Partial variance (c, d) describes the overall contribution of the parameter to model predictive uncertainty based on the combination of parameter uncertainty and model sensitivity.",
  "Input parameter distributions are shown in Figure 1."
)
readd(sensitivity_plot)
```

>>>>

```{r pairs-time, fig.cap = pairs_time_cap, fig.dim = c(8, 8)}
pairs_time_cap <- paste(
  htmlfig(),
  "Post-1975 growing season averaged NPP vs. LAI, with observation (in black)",
  "and linear regression, by model type.",
  "Letter labels are selected runs with the same parameters,",
  "and match the rows in Figure 4."
)
readd(pairs_time_averaged)
```

In most simulations, the leaf area index was too low for a given level of net primary productivity, but the relationship between these two variables varied with model configuration (Figure 3).
The crown model (closed vs. finite) had the strongest effect:
Compared to the simulations with "closed" crowns, simulations with finite canopy radius generally had lower net primary productivity for the same leaf area index.
Only a few individual simulations matched _both_ the observed leaf area index and net primary productivity, and all of them had the finite canopy radius configuration.

```{r bigfacet-plot, fig.cap = bigfacet_cap, fig.dim = c(12, 8)}
bigfacet_cap <- paste(
  htmlfig(),
  "PFT-level predictions of leaf area index (LAI) by model configuration and parameterization.",
  "Each row of plots is a simulation with the same set of parameters across model configurations.",
  "Letters correspond to the labels in Figure 3.",
  "Note that these are predictions of total leaf area index summed across all cohorts of the same PFT,",
  "meaning that higher LAI in one PFT does not necessarily indicate dominance, size, etc."
)
readd(lai_pft_plot)
```

@@

Model structure and parameters interacted to determine the community assembly and dynamics of each simulation, with consequences for overall ecosystem productivity that varied by model structure (Figure 4).
Consider simulations _A_ and _C_, the former showing competition of early hardwood with pine, and the latter completely dominated by pine:
With a closed canopy and static traits, both simulations produced similar overall LAI and NPP values (Figure 3), but moving to a finite canopy dramatically increased the total LAI in _C_ without much affecting _A_, while enabling trait plasticity dramatically increased the NPP of _A_ without much affecting _C_ (Figure 3).
This example also shows the impacts of different configurations on predicted community dynamics -- namely, in this specific case, enabling trait plasticity helped pine out-perform early hardwood, but only under a closed (rather than finite) canopy.
Finite canopy radius similarly benefits early hardwood in its competition against late hardwood in simulations _B_ and, to a lesser extent, _D_.
Simulations _B_ and _D_ also show that the sensitivity of a given parameter combination to model structure is itself dependent on the parameters -- simulation _B_ produced similar ecological dynamics and aggregate state variables regardless of model configuration (except the extreme cases; Figure 3), while simulation _D_ had near-zero NPP and LAI in two cases (closed, two-stream, static and finite, multi-scatter, plastic), comparable NPP and LAI to _B_ with closed canopy and trait plasticity, and higher NPP and LAI than _D_ with a finite canopy, multi-scatter radiative transfer, and static traits (Figure 3).

@@

Across all variables, parameter uncertainty (across ensembles within each model configuration) was at least as large, and usually larger, than structural uncertainty (Figure 4).
The relative importance of parameter uncertainty varied with both model configuration and the variable in question.
Facilitating horizontal competition by enabling the finite canopy radius (dark colors; compared to closed canopy -- light colors) reduced uncertainty in aboveground biomass, diversity, and primary productivity.
Using a multiple-scatter (secondary colors) rather than a two-stream (primary colors) radiative transfer scheme increased uncertainty in leaf area index, aboveground biomass, and diversity, but did not have a consistent effect on uncertainty in productivity.
Allowing SLA and V~cmax~ to vary with light level (warm colors, as opposed to static traits -- cool colors) had effectively no impact on simulation uncertainty (_but see caveat at the beginning of results_.)

```{r uncertainty-analysis, fig.cap = uncertainty_analysis_cap, fig.dim = c(20, 15)}
uncertainty_analysis_cap <- paste(
  htmlfig(),
  "PEcAn-like parameter sensitivity and uncertainty analysis, by model type.",
  "Elasticity (a, b) is the normalized sensitivity of the model to a fixed change in the parameter.",
  "Partial variance (c, d) describes the overall contribution of the parameter to model predictive uncertainty based on the combination of parameter uncertainty and model sensitivity.",
  "Input parameter distributions are shown in Figure 1."
)
readd(sensitivity_plot)
```
